Datasheet for 'Deaths of People Experiencing Homelessness' and 'Toronto Shelter System Flow

### 2024-04-18 other/datasheet/datasheet.qmd
fix date

---
title: "Datasheet for 'Deaths of People Experiencing Homelessness' and 'Toronto Shelter System Flow'"
author: 
  - Maroosh Gillani
thanks: "Code and data are available at: https://github.com/Maroosh-Gillani/homeless_mortality"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Datasheet for 'Deaths of People Experiencing Homelessness' and 'Toronto Shelter System Flow'"
author: 
  - Maroosh Gillani
thanks: "Code and data are available at: https://github.com/Maroosh-Gillani/homeless_mortality"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---
